%Понятие линейной деформации, допущения, понятия и эфекты
%Нелинейное деформ стержня, по времени
%Описать допущение что модуль упрогости = нелинейность 

\section*{Linear deformation}
For investigating motion of any mechanical system need to integrate equation of
motion\eqref{eqn:motionEq}. For this propose need to express all acting forces in
node\eqref{eqn:sumF} for each node in relation to their application place. 
\begin{equation}\label{eqn:sumF}
   F_n(X)=
   F_{ext}(X)+
   F_{elem}(x, y, z)\times[DCM]+
   F_{press}(x, y, z)\times[DCM]
\end{equation}\par
$F_{ext}$ is external load force, applied to node in global coordinates. Value
of this force for each time step is loaded from list of loads.\par $F_{press}$
is external pressure and can be described like force applied to element in local
coordinates. Value of this force for each time step is loaded from list of
loads.\par $F_{elem}$ is sum of internal forces of each element, which acting in
node. From each element counts only half of force to node, other half going to
neighbour node. In case of 1D element system, internal force of each element can
be express like axial force and it is equal to integral of stress over area:
\begin{equation}\label{eqn:Nx}
  N(x)= \int\limits_A \sigma dA
\end{equation}
For 1D rod system $F_{elem}$ can be expressed like:
\begin{equation}\label{eqn:Felem}
  F_{elem}= \sum_{e}N_e(x)/2
\end{equation}\par
The motion of nodes can be expressed by Newton's equation of motion. As 1D
element was choosed as discrete element, only the normal component of the
translational motion is considered, the equation reduces to\par
\begin{equation}\label{eqn:motionEq}
   F(x)-m\ddot{x}=0
\end{equation}
where $F(x)$ is axial force, equal to $F_n(X)$ for 1D rod system, $m$ – mass of
node and $\ddot{x}$ is acceleration, initial conditions are: $x(0)=0$ and
$\dot{x}(0)=V_0$.\par Equations of motion for Euler's scheme of integration can
be described like:
\begin{equation}\label{eqn:Accel}
  \ddot{U}(\Delta t)=Fn(X)/m
\end{equation}
\begin{equation}\label{eqn:Velos}
  \dot{U}(\Delta t)=\dot{U}(t)+\ddot{U}(\Delta t)\Delta t
\end{equation}
\begin{equation}\label{eqn:Displ}
  U(\Delta t)=U(t)+\dot{U}(\Delta t)\Delta t
\end{equation}
\par Element force becomes from physical deformation of
element. In linear case of study, deformation of element much less compare to
element dimensions. It is expressed by linear geometry
equation\eqref{eqn:linDeformation}, which showing relation between initial
length of element and length in $\Delta t$ state.
\begin{equation}\label{eqn:linDeformation}
  \varepsilon=\frac{dU}{dx}=\frac{l(\Delta t)-l_0}{l_0}
\end{equation}
According to Hook law $\sigma=\varepsilon E$ and linear geometry equation
\eqref{eqn:linDeformation}, inner force can be changed to:
\begin{equation}\label{eqn:linNxFull}
  N(x)= \int\limits_A \varepsilon EdA=EA\int \varepsilon=\frac{EA}{l_0}*(l(\Delta t)-l_0)
\end{equation}
where $l(\Delta t)$ is current length of element, $l_0$ length of element at
$t=0$, $E$ – Young’s modulus for element material. To be able to integrate
equation of motion, need to express deformation in equation
\eqref{eqn:linNxFull} by differences between displacements of nodes, to which
element is connected:
\begin{equation}\label{eqn:linNxWdispl}
  N(x)=\frac{EA}{l_0}*(U_{i}-U_{j})
\end{equation}\par
\section*{Nonlinear deformation}
Nonlinearity in main mean that element can get huge deformation compare to
element demesions. Equation of $F_{elem}$ in this case  would change to
nonlinear form:
\begin{equation}\label{eqn:nonlinNx}
  N(x)= \int\limits_t\int\limits_A \sigma dAdt
\end{equation}
From this equantion comes that cross sectional area and stiffness coefficient
will get nonlinearity.
 \par
%\subsection{Nonlinear cross sectional area}\par
Changing of cross sectional area over time for 1D element is changing its length
over time. Linear geometry equation\eqref{eqn:linDeformation}, showing linear
relations between length, because difference in $\Delta t$ state takes according
initial length of element. In case of huge deformation need to recalculate
length of element on each time step and take difference of displacement
according to previous time step. In end of geometry equation become to nonlinear
form:
\begin{equation}\label{eqn:nonlinDeformation}
  \varepsilon=\frac{dU}{dx}=\frac{l(\Delta t)-l(t-\Delta t)}{l(\Delta t)}
\end{equation}
Inner force\eqref{eqn:linNxFull} also become to nonlinear form:
\begin{equation}\label{eqn:nonlinNxFull}
  N(x)= \int\limits_t\int\limits_A \varepsilon EdA=EA\int\limits_t\varepsilon=\frac{EA}{l(\Delta t)}*(l(\Delta t)-l(t-\Delta t))
\end{equation}
where $l$ is current length of element, $l_0$ length of element at $t=0$, $E$ –
Young’s modulus for element material.\par And nonlinear equantion of inner force
for integration:
\begin{equation}\label{eqn:nonlinNxWdispl}
  N(x)=\frac{EA}{l_0}*(U_{i}-U_{j})
\end{equation}\par

\subsection{Nonlinear behavior model}\par
Mooney-Rivlin models are popular for modeling the large strain nonlinear
behavior of incompressible materials. According to thermodynamics laws, the
2nd Piola-Kirchhoff stress is the partial derivative of the Helmholtz free
energy with respect to the elastic part of the Green strain tensor (with a
density thrown in).
\[
\boldsymbol{\sigma}^\text{PK2} = \rho_o \, {\partial \Psi \over \partial {\bf
E}^\text{el} }
\]
The Helmholtz free energy contains thermal energy and mechanical strain
energy.  
But in most every discussion of Mooney-Rivlin coefficients, the thermal part
is neglected, leaving only the mechanical part, \(W\).  (Actually, \(W\) is
declared to represent \(\rho_o \Psi\), not just \(\Psi\)).  Second, since all
of the deformation of a hyperelastic material is elastic by definition, it is
sufficient to write \({\bf E}^\text{el}\) simply as \({\bf E}\). This gives
\[
\boldsymbol{\sigma}^\text{PK2} = {\partial W \over \partial {\bf E} }
\]
But there is a challenge with this general approach.  It is the determination
of off-diagonal (shear) terms.  As with the shear terms in Hooke's Law, they
are not independent of the normal terms, but must be consistent with
coordinate transformations that transform normal components into shears and
vice-versa. And as with Hooke's Law, the resolution is to define the material
behavior for the principal values and rely on coordinate transformations to
give the appropriate corresponding behavior of the shear terms.
\[
\sigma_i^\text{PK2} = {\partial W \over \partial E_i }
\]
But alas, even this is not quite what is done in Mooney-Rivlin models.
Instead, derivatives are taken with respect to <i>stretch ratios</i>,
\(\lambda\), which are the ratios of initial and final lengths in the
principal directions, \((L_F / L_o)\).  So the stretch ratio is "one plus
engineering strain,"  \(\lambda = 1 + \epsilon_{Eng}\), and therefore
\(\lambda - 1 = \epsilon_{Eng} = \Delta L \, / L_o\).

According to Mooney-Rivlin model and geometry equation
\eqref{eqn:deformation}, inner force can be changed to
\begin{equation}\label{eqn:nNxFull} N(x)= \int\limits_A \varepsilon EdA=EA\int
\varepsilon=\frac{EA}{l_0}*(l-l_0) \end{equation} where $l$ is current length
of element, $l_0$ length of element at $t=0$, $E$ – Young’s modulus for
element material. To be able to integrate equation of motion, need to express
deformation in equation \eqref{eqn:nNxFull} by differenses between
displacements of nodes, to which element is connected:
\begin{equation}\label{eqn:nNxWdispl} N(x)=\frac{EA}{l_0}*(U_{i}-U_{j})
\end{equation}\par Equations of motion for integrating \eqref{eqn:Accel},
\eqref{eqn:Velos},\eqref{eqn:Displ} would be same as in linear
case\textcite{Picault2014}. \par
\newpage